### 2014-06-26 4/polsar.tex
auto

\section{Consistent Measures of Distance for POLSAR data}

@@

Theoretical simulations of the models based on Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are also performed.
The nominal value of 4 was taken as the dataset's number of looks, $L$, while the
dimensional number $d$ is set to 3 for the full polarimetric SAR dataset, and 2 for the partial polarimetric SAR dataset. 
The histogram plots of the theoretical models and the real-life dataset are presented in Fig. \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast}. A visual match is clearly observable which verifies the applicability of
the theoretical models for the dispersion and contrast measures of distance.

\begin{figure}[bth!]
\centering
\begin{tabular}{c}
	\subfloat[part-pol (2x2) dispersion]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
		 \label{dispersion_2x2}
	} 
	\hfill	
	\subfloat[part-pol (2x2) contrast]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
		 \label{contrast_2x2}
	} \\
	\subfloat[full-pol (3x3) dispersion]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
		 \label{dispersion_3x3}
	} 
	\hfill	
	\subfloat[full-pol (3x3) contrast]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
		 \label{contrast_3x3}
	}
\end{tabular}
\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
\end{figure}

>>>>

\section{Consistent Measures of Distance for POLSAR data}
\label{sec:consistent_measures_distance_polsar}

@@

Theoretical simulations of the models based on Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are also performed.
The nominal value of 4 was taken as the dataset's number of looks, $L$, while the
dimensional number $d$ is set to 3 for the full polarimetric SAR dataset, and 2 for the partial polarimetric SAR dataset. 
The histogram plots of the theoretical models and the real-life dataset are presented in Fig. \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast}. A visual match is clearly observable which verifies the applicability of
the theoretical models for the dispersion and contrast measures of distance.
This qualitative observation is further supported by high significance level (or p-value) in the standard Kolmogorov-Smirnov goodness-of-fit test between curves \cite{Kolmogoroff_1941_AMS_461}, noted under each graph.
While a good p-value may not lead to automatic acceptance of the model, high p-values lend a high level of confidence to the proposal.

\begin{figure}[bth!]
\centering
\begin{tabular}{c}
	\subfloat[part-pol (2x2) dispersion (p-value HH-HV=0.????)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
		 \label{dispersion_2x2}
	} 
	\hfill	
	\subfloat[part-pol (2x2) contrast (p-value HH-HV=0.9182)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
		 \label{contrast_2x2}
	} \\
	\subfloat[full-pol (3x3) dispersion (p-value=0.????)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
		 \label{dispersion_3x3}
	} 
	\hfill	
	\subfloat[full-pol (3x3) contrast (p-value=0.9254)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
		 \label{contrast_3x3}
	}
\end{tabular}
\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.
Each histogram plots the signal(s) under investigation against its probabilistic distribution across the patch,
  with p-value being the significance level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms.  
}
\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
\end{figure}

### 2014-06-26 6/conclusional_discussion.tex
auto

  Chapter \ref{chap:sar} then presents homoskedastic models that are derived for heteroskedastic SAR data. 
In Chapter \ref{chap:polsar}, scalar and representative statistical models are proposed for the multi-dimensional and inter-correlated POLSAR data.
These two seemingly disconnected results are unified, when the statistical models for POLSAR are shown to be the generic multi-dimensional extension of the commonly used statistical models for SAR intensity.
This combination leads to the main result: the proposal of scalar, representative and homoskedastic models for both SAR and POLSAR data.
These theoretical results are applied in chapter \ref{chap:applications} where a new clustering algorithm and a new SAR speckle filter are proposed together with our proposal of using MSE to evaluate both SAR and POLSAR speckle filters.

%What are the results?
Generally speaking, this thesis contributes solutions for the problem of how to interpret and process the multidimensional and stochastic (POL)SAR data.
%One way of contribution is to derive new and better techniques to help alleviate the situation.
%The most direct way of contributing to this problem is to
%as well as derives new and
%better techniques to process the data. %help alleviate the situation. 
%An even better way, however, is to derive new theoretical models from which novel data processing technique can be derived.
%In this thesis, new theoretical models are derived for the (POL)SAR data
%  in addition to several novel (POL)SAR data processing techniques
%  which are also proposed as beneficial applications of these models.
Specifically, the
                main theoretical results obtained in this thesis are novel statistical
                models, which subsequently lead to derivation of
                consistent and homoskedastic measures of distance, for
                both SAR and POLSAR data.
Compared
                to other scalar models for POLSAR the proposed models
                are highly representative of the multi dimensional data.
Its
                representative power is demonstrated as it lead to
                consistent discrimination measures as well as it
                generalizes the traditional representative model for SAR
                intensity towards the multidimensional domain.

%It is common-consensus that in the original multiplicative SAR domain,
%  the intensity ratio serves as the best available discrimination measure.
%Meanwhile, there are several proposed discrimination measures for POLSAR
%  but there are no apparent link between the two fields.
%This thesis shows that the logarithmic transformation not only converts multiplicative SAR into 
The proposal of using the determinant ratio as a POLSAR discrimination measure is also a novel contribution.
It can be considered as the extension of the SAR intensity ratio,
  which have long been considered as the best discrimination measures for traditional SAR data \cite{Rignot_1993_TGRS_896}.
It works consistently in the original multiplicative and heteroskedastic POLSAR domain,
  and the logarithmic transformation converts this ratio into a consistent subtractive measures of distance in the transformed additive and homoskedastic domain.
This
                derived consistent measures of distance for SAR and
                especially for POLSAR are also a novelty.
With regards to other existing discrimination measures for SAR and POLSAR,
                this thesis unite them, together with the new ones
                proposed herein, all into a consistent theory.
%More
%                over the homoskedastic models and their derived
%                consistent measures of distance bring about the benefits
%                of homoskedastic statistical estimation framework.

@@

@@

The work in this research results in the following list of articles that has been prepared for public communication:

\begin{enumerate}
\item \textbf{Neural network-assisted reconstruction of full polarimetric SAR information.}
  Thanh-Hai Le, I. McLoughlin, Ken Yoong Lee, and T. Bretschneider.
  In \textit{Communications, Control and Signal Processing (ISCCSP), 2010 4th International Symposium on}, pages 1–5, 2010.  \cite{Le_2010_ISCCSP} 
\item \textbf{SLC SAR speckle filtering using homoskedastic features of logarithmic transformation.}
  T. H. Le, I. V. McLoughlin, K. Y. Lee, and T. Brestchneider.
  In \textit{Proceedings of the 31st Asian Conference on Remote Sensing (ACRS)}, Hanoi, Vietnam, Nov 2010. \cite{Le_2010_ACRS}
\item  \textbf{SAR Fuzzy-MLE Speckle Filter using the Distance Consistency Property in Homoskedastic Log-Transformed Domain.}
  T. H. Le and I. V. McLoughlin. 
  In \textit{Proceedings of the 32nd Asian Conference on Remote Sensing (ACRS)}, Taipei, Taiwan, Nov 2011 \cite{Le_2011_ACRS}
\item \textbf{Scalar and Representative Models for Polarimetric SAR Data.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun,
  re-submitted to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
\item \textbf{Using MSE to evaluate SAR speckle filters.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun.
  submitted to \textit{IET Radar, Sonar \& Navigation}
\end{enumerate}

>>>>

 Chapter \ref{chap:sar} then presents homoskedastic models that are derived for heteroskedastic SAR data. 
In Chapter \ref{chap:polsar}, scalar and representative statistical models are proposed for the multi-dimensional and inter-correlated POLSAR data.
These two seemingly disconnected results are unified, when the statistical models for POLSAR are shown to be the generic multi-dimensional extension of the commonly used statistical models for SAR intensity.
This combination leads to the main result: the proposal of scalar, representative and homoskedastic models for both SAR and POLSAR data.
These theoretical results are applied in Chapter \ref{chap:applications} where a new clustering algorithm and a new SAR speckle filter are proposed together with our proposal of using MSE to evaluate both SAR and POLSAR speckle filters.

%What are the results?
Generally speaking, this thesis contributes solutions for the problem of how to interpret and process the multidimensional and stochastic (POL)SAR data.
%One way of contribution is to derive new and better techniques to help alleviate the situation.
%The most direct way of contributing to this problem is to
%as well as derives new and
%better techniques to process the data. %help alleviate the situation. 
%An even better way, however, is to derive new theoretical models from which novel data processing technique can be derived.
%In this thesis, new theoretical models are derived for the (POL)SAR data
%  in addition to several novel (POL)SAR data processing techniques
%  which are also proposed as beneficial applications of these models.
Specifically, the
                main theoretical contributions obtained in this thesis are novel statistical
                models, which subsequently lead to derivation of
                consistent and homoskedastic measures of distance, for
                both SAR and POLSAR data.
Compared
                to other scalar models for POLSAR the proposed models
                are highly representative of the multi dimensional data.
Its
                representative power is demonstrated as it lead to
                consistent discrimination measures as well as it
                generalizes the traditional representative model for SAR
                intensity towards the multidimensional domain.

%It is common-consensus that in the original multiplicative SAR domain,
%  the intensity ratio serves as the best available discrimination measure.
%Meanwhile, there are several proposed discrimination measures for POLSAR
%  but there are no apparent link between the two fields.
%This thesis shows that the logarithmic transformation not only converts multiplicative SAR into 
The proposal of using the determinant ratio as a POLSAR discrimination measure is also a novel contribution.
It can be considered as the extension of the SAR intensity ratio,
  which have long been considered as the best discrimination measures for traditional SAR data \cite{Rignot_1993_TGRS_896}.
It works consistently in the original multiplicative and heteroskedastic POLSAR domain,
  and the logarithmic transformation converts this ratio into a consistent subtractive measures of distance in the transformed additive and homoskedastic domain.
This
                derived consistent measures of distance for SAR and
                especially for POLSAR are also a novelty.
With regards to other existing discrimination measures for SAR and POLSAR,
                this thesis unites them, together with the new ones
                proposed herein, all into a consistent theory.
%More
%                over the homoskedastic models and their derived
%                consistent measures of distance bring about the benefits
%                of homoskedastic statistical estimation framework.

@@

Corresponding to the objectives outlined in Chapter 1,
  the following results have been obtained:
\begin{enumerate}
\item           Several scalar and highly representative statistical models
                for the multi-dimensional and inter-correlated POLSAR
                data have been proposed:
                \begin{enumerate}
                \item The determinant statistical model is established for the determinant of POLSAR covariance matrices (Section \ref{sec:polsar_heterosked_model_and_log_transform}),
                \item Several statistical models for different discrimination measures (namely: determinant-ratio, log-distance, dispersion and contrast) are derived together with its consistent property (Section \ref{sec:consistent_measures_distance_polsar}). %being modelled 
                \item The proposed models for POLSAR are also shown to include the traditional SAR statistical models (Section \ref{sec:sar_special_case_of_polsar}).
                \item \label{itm:polsar_validation} The proposed models are validated against practical real-life
                captured POLSAR data in Section \ref{sec:polsar_models_validation}.
                \end{enumerate}
\item                Homoskedastic statistical models for the
                heteroskedastic (POL)SAR data are derived. Specifically 
                \begin{enumerate}
                \item \label{itm:log_transform} The statistical model for POLSAR data are shown to be heteroskedastic in
                the original domain and logarithmic transformation
                converts this into a homoskedastic model (Sections \ref{sec:heteroskedastic_sar}, \ref{sec:homoskedastic_sar}, \ref{sec:polsar_heterosked_model_and_log_transform}).
                \item \label{itm:sar_measures_distance} Homoskedastic measures of distance for
                the multi dimensional POLSAR as well as for the one
                dimensional SAR data are derived (Sections \ref{sec:consistent_measures_distance_sar}, \ref{sec:consistent_measures_distance_polsar})
                \item \label{itm:sar_validation} These statistical models are validated against both
                practical SAR and POLSAR data (Sections: \ref{sec:sar_special_case_of_polsar}, \ref{sec:polsar_models_validation})
                \end{enumerate}
\item The beneficial applications of these
                statistical models have also been demonstrated. Specifically:
                \begin{enumerate}
                \item \label{itm:filter_vicious_circle} The consistent sense of variance
                is shown to help breaking the vicious cycle in the problem of SAR
                speckle filtering: with new statistical test for
                homogeneity and new speckle filters proposed (Section \ref{sec:k_mle}, \ref{sec:f_mle}).
                \item \label{itm:log_mse} Tconsistent sense of subtractive
                distance also helps in the problem of evaluating SAR
                speckle filters. Section \ref{sec:sar_filters_evaluation} proposes the use of the log-MSE to combine the
                evaluation of radiometric preservation and speckle
                suppression power in evaluating SAR speckle filters.
                \item \label{itm:extend_sar_to_polsar} Section \ref{sec:polsar_models_validation} demonstrates an example where the existing SAR
                processing technique of ENL estimation is extended towards POLSAR data.
                \end{enumerate}
\end{enumerate}

@@

The work in this research results in the following list of articles that have been prepared for public communication:

\begin{enumerate}
\item \textbf{Neural network-assisted reconstruction of full polarimetric SAR information.}
  Thanh-Hai Le, I. McLoughlin, Ken Yoong Lee, and T. Bretschneider.
  In \textit{Communications, Control and Signal Processing (ISCCSP), 2010 4th International Symposium on}, pages 1–5, 2010.  \cite{Le_2010_ISCCSP} 
\item \textbf{SLC SAR speckle filtering using homoskedastic features of logarithmic transformation.}
  T. H. Le, I. V. McLoughlin, K. Y. Lee, and T. Brestchneider.
  In \textit{Proceedings of the 31st Asian Conference on Remote Sensing (ACRS)}, Hanoi, Vietnam, Nov 2010. \cite{Le_2010_ACRS}
\item  \textbf{SAR Fuzzy-MLE Speckle Filter using the Distance Consistency Property in Homoskedastic Log-Transformed Domain.}
  T. H. Le and I. V. McLoughlin. 
  In \textit{Proceedings of the 32nd Asian Conference on Remote Sensing (ACRS)}, Taipei, Taiwan, Nov 2011 \cite{Le_2011_ACRS}
\item \textbf{Scalar and Representative Models for Polarimetric SAR Data.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun,
  under revision for resubmission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}

\item \textbf{Using MSE to evaluate SAR speckle filters.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun.
  submitted to \textit{IET Radar, Sonar \& Navigation}
\end{enumerate}
